Reproducibility in plant pathology: where do we stand and a way forward

### 2021-07-21 analysis/paper/paper.Rmd
Reknit paper with final contributions uncommented
Replace "subjective" with "objective"
Correction suggested by Dr David Ferris, Farming Systems Innovation, DPIRD

We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely subjective.
We have based our scoring decisions on our own experiences in the field of plant pathology.
While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.

@@

A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
N.J.G. provided five-year impact factors.
A.H.S., E.DP., Z.F. and K.dSA. evaluated articles for scoring.
A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
A.H.S. wrote the manuscript in consultation with E.DP.
<!-- All authors provided critical feedback and helped contribute to the final version of the manuscript. -->

>>>>

We recognise that the scoring methods were developed by the authors specifically for this exercise and are not entirely objective.
We have based our scoring decisions on our own experiences in the field of plant pathology.
While many software packages may be widely used or "freely" available if one has an institutional license, these types of software often hinder partners and interested parties that do not have these luxuries.
Thus, the emphasis was given to using open source alternatives where possible over commercially available, non-free software packages.
The view of the authors is one that this is something to be encouraged as it allows the broadest possible audience to benefit from the work at the lowest possible cost.

@@

A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
N.J.G. provided five-year impact factors.
A.H.S., E.DP., Z.F. and K.dSA. evaluated articles for scoring.
A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
A.H.S. wrote the manuscript in consultation with E.DP.
All authors provided critical feedback and helped contribute to the final version of the manuscript.
